Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-24 WSSSPE2_report/WSSSPE2_review.tex
Section 3.1: Use past tense.

Hong drew attention to the misconception that we too often disregard hundreds of
thousands of software researchers thinking they are the long tail. We forget
that actually they are the mainstream and we are the elite minority. He
emphasized that software is no longer special; it is prevailing in scientific
research. Survey of researchers from 15 Russell Group universities conducted by
the SSI between Aug--Oct 2014 included a total of 406 respondents covering a
representative range of funders, disciplines, and seniority: 92\% confirmed the
use of research software such as MATLAB, SPSS, Excel, so on and so forth; 89\%
affirmed that it would be impossible or difficult to conduct research without
software. %Researchers often discover new software predominatly through
%recommendation of colleagues or web searches.
Nevertheless the British research community is just starting to understand the
magnitude of the issue. In the aforementioned SSI survey, 56\% of  
researchers develop their own research software; 71\%  have had
no formal software -development training; 140,000 researchers rely on
their own coding skills; 4\% of jobs advertised in British universities were software
related.

>>>>

Hong drew attention to the misconception that we too often disregard hundreds of
thousands of software researchers thinking they are the long tail. We forget
that actually they are the mainstream and we are the elite minority. He
emphasized that software is no longer special; it is prevailing in scientific
research. Survey of researchers from 15 Russell Group universities conducted by
the SSI between Aug--Oct 2014 included a total of 406 respondents covering a
representative range of funders, disciplines, and seniority: 92\% confirmed the
use of research software such as MATLAB, SPSS, Excel, so on and so forth; 89\%
affirmed that it would be impossible or difficult to conduct research without
software. %Researchers often discover new software predominatly through
%recommendation of colleagues or web searches.
Nevertheless the British research community is just starting to understand the
magnitude of the issue. In the aforementioned SSI survey, 56\% of  
researchers developed their own research software; 71\%    had
no formal software-development training; 140,000 researchers relied on
their own coding skills; 4\% of jobs advertised in British universities were software
related.
